\section{Module 1 --- On-Chain Data Extraction}
\label{sec:module1}

Module 1 builds the raw on-chain data layer used by all later analysis on the pool mentioned in the introduction.  The swap study window is from 
the \date{1st of October 2025} to the \date{31st of March 2026}, while liquidity-changing events are read from
the pool deployment block, 12,376,729, so that the opening liquidity map can
be reconstructed from the full history of Mint and Burn events.

\subsection{Extracted Files}
\label{subsec:m1-files}

All event data was extracted directly using Ethereum archive-node RPC calls, with 
the dedicated extraction script resolving the study-window blocks from UTC timestamps,
downloading raw pool logs, decoding them with the pool ABI, resolving timestamps once
per unique block, and writing them to compact Parquet files.  All four required files are
reproduced from scratch by a single documented entry point,
\path{src/module1/data_extraction.py}, which takes as inputs an archive RPC
endpoint URL and the desired pool address (\texttt{data\_extraction.py extract all}). 
The output data dictionary can be found in the repository's README.

The main swap file, \path{swap_events.parquet}, contains \num{1,095,286} decoded swaps
across 637,982 unique blocks. Their precise timestamp range is
\date{2025-10-01 00:00:11 UTC} to \date{2026-03-31 23:59:59 UTC} meaning the file data is bounded by
the required six-month window. The underlying cumulative swap volume is nearly balanced, with 534,929 swaps as
\path{buy_weth} and 560,357 as \path{sell_weth}. Aggregating absolute USDC
notional gives a total pool volume of \$$21.39$ billion USDC over the sample, split
almost evenly between buys (\$10.70 billion) and sells (\$10.69 billion). 
This allows us to compare with the decoded trade direction convention and 
gives no indication of missing sign flips or decimal-scaling errors.

In the liquidity event file, \path{mint_burn_events.parquet}, there are \num{427,934}
events, from contract deployment through to the end of the study window, with \num{204,398} Mints and
\num{223,536} Burns. The support file \path{collect_events.parquet} contains \num{218,219}
Collect events over the same historical range and is used later for fee
analytics.  The daily state files contain \num{182} midnight-UTC snapshots, where
\path{slot0_snapshots.parquet} stores the pool price and active tick, while
\path{liquidity_snapshots.parquet} stores \num{264,149} the initialized-tick rows,
averaging around \num{1,451} ticks per snapshot.

\subsection{Validation}
\label{subsec:m1-validation}

We first apply schema and coverage checks to every generated file. These checks
verify the required columns, reject duplicate event identities
(\path{tx_hash}, \path{log_index}), require valid tick spacing and Mint/Burn
signs thereby confirming that both slot0 and liquidity snapshots cover exactly 182
daily blocks. All checks pass on the submitted files.

The volume cross-check aggregates decoded swaps by direction and compares the
resulting totals against the event-level signs.  Since USDC is token0, a
\path{buy_weth} swap has positive USDC flow into the pool whereas a \path{sell_weth}
swap has positive WETH flow into the pool. Therefore the aggregate absolute USDC amount
equals the reported USD notional total, \$$21.39$ billion, and the buy/sell
notional split differs by less than \num{0.2}\%.  Table~\ref{tab:m1-volume} reports the cross-check by
direction with the buy/sell notional split differing by only \num{0.061}\%, and the
aggregate absolute USDC amount equaling the reported USD notional total to the
displayed precision.

\begin{table}[t]
    \centering
    \small
    \caption{Volume cross-check on \protect\path{swap_events.parquet} (1 Oct 2025 -- 31 Mar 2026).}
    \label{tab:m1-volume}
    \begin{tabular}{lrr}
        \toprule
        Direction & Swaps & Absolute USDC notional (USD bn) \\
        \midrule
        \path{buy_weth}  &   534{,}929 & 10.702 \\
        \path{sell_weth} &   560{,}357 & 10.690 \\
        \midrule
        Total            & 1{,}095{,}286 & 21.392 \\
        \bottomrule
    \end{tabular}
\end{table}

We also compare each daily slot0 price with the most recent decoded swap price
at or before the snapshot block. The validation table contains \num{181} comparable
snapshots, \num{180} of these being within the 1 bp tolerance used by the script. The median
absolute difference is \num{0.0000} bps, and the 95th percentile is \num{0.0018} bps.  The
only larger row is \num{11.71} bps on the snapshot from \date{2026-02-05}, where the comparison
swap is in the same block as the snapshot.  This appears to be a same-block
ordering edge case in the diagnostic table rather than a systematic price
conversion problem: the remaining comparisons are effectively exact.
Table~\ref{tab:m1-slot0} summarizes the full check, saved to
\path{data/results/module_1/slot0_swap_price_check.parquet}.

\begin{table}[t]
    \centering
    \small
    \caption{Daily slot0 price vs.\ last decoded swap price before the snapshot block.}
    \label{tab:m1-slot0}
    \begin{tabular}{lr}
        \toprule
        Statistic & Value \\
        \midrule
        Comparable snapshots                 & 181 \\
        Within 1 bp tolerance                 & 180 \\
        Median absolute difference (bps)      & 0.0000 \\
        95th percentile absolute diff.\ (bps) & 0.0018 \\
        Maximum absolute difference (bps)     & 11.71 \\
        Snapshot of the maximum               & 2026-02-05 (same block) \\
        \bottomrule
    \end{tabular}
\end{table}

Finally, the reconstructed liquidity map is checked against direct archive
\path{pool.ticks()} calls.  At snapshot block \num{23,479,243}, we sampled \num{10} 
initialized ticks from \path{liquidity_snapshots.parquet} and queried the pool
contract at that same historical block.  Both \path{liquidityGross} and
\path{liquidityNet} matched exactly for all \num{10} sampled ticks. This confirms
that replaying the Mint and Burn history reconstructs the on-chain tick state at
the snapshot block, with no discrepancies found in the spot-check.
Table~\ref{tab:m1-ticks} lists the sampled ticks; the persisted artifact
\path{data/results/module_1/liquidity_tick_spot_check.parquet} contains the full
reconstructed and on-chain values for both \path{liquidityGross} and
\path{liquidityNet}, which are bit-for-bit equal for every sampled tick.


\begin{table}[t]
    \centering
    \small
    \caption{Reconstructed tick state vs.\ direct archive \protect\path{pool.ticks()} at block 23{,}479{,}243. Values shown to 4 significant figures; the persisted artifact stores exact integers and all rows match exactly on both \protect\path{liquidityGross} and \protect\path{liquidityNet}.}
    \label{tab:m1-ticks}
    \begin{tabular}{rrrc}
        \toprule
        Tick & $L_{\mathrm{gross}}$ & $L_{\mathrm{net}}$ & On-chain match \\
        \midrule
        $-887{,}270$ & $2.308{\times}10^{16}$ & $+2.308{\times}10^{16}$ & Yes \\
        $-92{,}110$  & $3.983{\times}10^{11}$ & $+3.983{\times}10^{11}$ & Yes \\
        $-76{,}280$  & $2.965{\times}10^{19}$ & $+2.965{\times}10^{19}$ & Yes \\
        $-75{,}980$  & $2.965{\times}10^{19}$ & $-2.965{\times}10^{19}$ & Yes \\
        $0$          & $1.357{\times}10^{13}$ & $+1.357{\times}10^{13}$ & Yes \\
        $100$        & $100$                  & $+100$                  & Yes \\
        $110$        & $100$                  & $-100$                  & Yes \\
        $100{,}000$  & $1.357{\times}10^{13}$ & $-1.357{\times}10^{13}$ & Yes \\
        $108{,}340$  & $2.267{\times}10^{9}$  & $+2.267{\times}10^{9}$  & Yes \\
        $108{,}360$  & $2.274{\times}10^{9}$  & $+2.274{\times}10^{9}$  & Yes \\
        \bottomrule
    \end{tabular}
\end{table}
